Reproducibility of SNV-calling in multiple sequencing runs from single tumors

### 2015-10-23 PAPER/paper.tex
finished revisions

>>>>

For all alignments, average read coverage was 30X, with a low of 5X and a high of 60X (stdev=15.95898). The percentage of mapped reads in our alignments was universally high (mean=98.03545, stdev=3.257872), with only two samples below 90\% (68\% and 74\%), and only 15 samples below 98\%. We found no correlation between the read coverage or the percentage of mapped reads and the total number of SNVs called (Supplementary Figures 2 and 3).
